Assessment and Optimization of Nowcast Measures for Trend Detection

### 2023-12-12 paper.tex
Update plots

\newcommand{\lag}[1][l]{\Delta_{#1}}
\DeclarePairedDelimiter{\abs}\lvert\rvert
\DeclareMathOperator{\sign}{sign}
\newcommand{\tmax}{\bar{t}}
\newcommand{\ind}[1]{\mathbbm{1}\{#1\}}
\newcommand{\ydiff}{\overset{\triangle}{y}}
\newcommand{\ydifft}{\overset{\triangle}{y}^*}
\newcommand{\xdiff}{\overset{\triangle}{x}}
\newcommand{\xdifft}{\overset{\triangle}{y}^*}
\newcommand{\Ydiff}{\overset{\triangle}{Y}}
\newcommand{\Xdiff}{\overset{\triangle}{X}}
\newcommand{\Prob}[1]{P(#1)}
\newcommand{\mprob}{\tilde{m}}

@@

@@

\begin{itemize}
  \item Bootstrapping: Describe approach (Simple bootstrap or multiplier?)
  \item Missing data
\end{itemize}

@@

\begin{figure}
  \centering
  \includegraphics{plots/simulation_same_rmse_mae/4q_plot.pdf}
  \caption{4Q-Plot for Simulation~\ref{sec:simulation_rmse_mae} with $T = 100$, $\sigma_y=0.1$, $a = 10$, $p_2 = 0.8$, and $p_3 = (0.8, 0.4)$.}
  \label{fig:simulation_rmse_mae_4q}
\end{figure}

@@

Question: How well does bootstrap approach perform?

\begin{itemize}
  \item Auf jeden Fall
\end{itemize}

>>>>

\newcommand{\lag}[1][l]{\Delta_{#1}}
\DeclarePairedDelimiter{\abs}\lvert\rvert
\DeclareMathOperator{\sign}{sign}
\newcommand{\tmax}{\bar{t}}
\newcommand{\ind}[1]{\mathbbm{1}\{#1\}}
\newcommand{\ydiff}{\overset{\triangle}{y}}
\newcommand{\ydifft}{\overset{\triangle}{y}^*}
\newcommand{\xdiff}{\overset{\triangle}{x}}
\newcommand{\xdifft}{\overset{\triangle}{y}^*}
\newcommand{\Ydiff}{\overset{\triangle}{Y}}
\newcommand{\Xdiff}{\overset{\triangle}{X}}
\newcommand{\Prob}[1]{P(#1)}
\newcommand{\mprob}{\tilde{m}}
\newcommand{\Ber}{\text{Ber}}
\newcommand{\SBer}{\text{SBer}}

@@

\hl{How to determine $\sigma$?}

@@

\begin{itemize}
  \item Bootstrapping: Compare percentile and BCa approach?
  \item Bootstrapping: What is the \enquote{true} value?
  \item Missing data
\end{itemize}

@@

\begin{figure}
  \centering
  \begin{subfigure}{.32\textwidth}
  	\includegraphics{plots/simulation_same_rmse_mae/4q_plot_1}
  \end{subfigure}
  \begin{subfigure}{.32\textwidth}
  	\includegraphics{plots/simulation_same_rmse_mae/4q_plot_2}
  \end{subfigure}
    \begin{subfigure}{.32\textwidth}
  	\includegraphics{plots/simulation_same_rmse_mae/4q_plot_3}
  \end{subfigure}
  \caption{4Q-Plot for Simulation~\ref{sec:simulation_rmse_mae} with $T = 100$, $\sigma_y=0.1$, $a = 10$, $p_2 = 0.8$, and $p_3 = (0.8, 0.4)$.}
  \label{fig:simulation_rmse_mae_4q}
\end{figure}

@@

Simulation setup:

\begin{itemize}
  \item $T = 10,000$
  \item $\ydiff_t \sim N(0, 1)$ 
  \item $\xdiff_t^{1, k} = b_t  \ydiff_t, b_t \sim \SBer(k)$ (symmetric Bernoulli)
  \item \hl{(or both + random (non-systematic) noise?)}
\end{itemize}

Analysis:
\begin{itemize}
\item Do for $l = 1, \dots, 1,00$:
\begin{itemize}
  \item Sample $\ydiff, \xdiff$
  \item Compute bootstrap confidence intervals $(b_{low}, b_{up})_l$ using $B = 10,000$
\end{itemize}
  \item Visualize all intervals with real value (confidence interval should cover real value in $\alpha$ cases)
\end{itemize}
